Demystifying the Combination of Dynamic Slicing and \\ Spectrum-based Fault Localization

### 2019-02-24 paper/ijcai/paper.tex
rw

% \Rui{Introductory sentences should say something like: model-based software
% debugging, from the DX community, has been shown to be similar to slicing
% Mayer and Stumptner, 2008; Wotawa and Nica; etc. Having said that, not many
% interesting techniques having been pursued because of scalability. We have
% achieved it with a type of program slicing --- critical slicing. Next, we
% visit the previous works on program slicing and SFL, without the idea of
% being exhaustive, but merely discussing the works that we deem relevant for
% this paper.}
%
% \Rui{revisit sentences; check if recent papers are cited.}

% \subsection{Program Slicing}
%
% Program Slicing is an old technique with several applications in PL
% and SE research~\cite{Weiser:1981:PS:800078.802557}. Slicing can be
% implemented in different ways. Dynamic Slicing has found its main
% application in fault
% localization~\cite{Agrawal:1990:DPS:93542.93576}---in this application
% context, failing tests exist. Research in this area has mainly focused
% on slicing code
% efficiently~\cite{Wang:2008:DSJ:1330017.1330021,Wang:2004:UCB:998675.999455}
% and avoiding data and control omission
% errors~\cite{Zhang:2007:TLE:1250734.1250782,Lin:2018:BDE:3238147.3238163}. Omission errors correspond to the
% cases where tests fail because some part of the code was not executed
% when it should. Dynamic fault localization techniques cannot hope to
% soundly report bugs in those cases. The issue is that incorporating
% static information to capture those cases can result in unacceptably
% large slices, which defeats the purpose of reducing the fault search
% space. It is worth noting that, conceptually, the \sfl{}+\ds{} combination
% can be used with any form of dynamic slicing. We chose an
% implementation of Critical
% Slicing~\cite{DeMillo:1996:CSS:229000.226310} for its generality.
%
%
% \subsection{SFL}
%
% Statistics-based techniques (e.g., ~\cite{Pearson:2017:EIF:3097368.3097441}) are
% popular automated fault localization techniques within the Software Engineering
% community. They correlate information about program fragments that have been
% exercised in multiple program execution traces (also called \textit{program
% spectra}) with information about successful and failing executions. By doing
% that, statistics-based approaches yield a list of suspect program fragments
% sorted by their likelihood to be at fault. Since this technique is efficient in
% practice, it is attractive for large modern software systems ~\cite{Zoeteweij:2007:DES:1251988.1253298}.
%
% Spectrum-based fault localization (\sfl{}) is amongst the most common statistical
% fault localization technique that takes as input a test suite including at least
% one failing test and reports on output a ranked list of components likely to be
% in fault ~\cite{7390282,DBLP:conf/kbse/JonesH05,DBLP:journals/smr/LuciaLJTB14,DBLP:journals/jss/AbreuZGG09}.
%
% \subsection{Combination of \sfl{} and Slicing}
%
% Prior work has investigated the combination of dynamic slicing and
% spectrum-based fault
% localization ~\cite{Wotawa:2010:FLB:1848650.1849235,Alves:2011:FUD:2190078.2190115,DBLP:conf/ecai/HoferW12,lei-mao-dai-wang-2012,slicing-sfl-repair}. Although
% the methodology used in these papers vary, the overall message is that
% the combination is valuable. Note that slicing alone does not provide
% the guarantee of improvement to \sfl{} as statements discarded with
% slicing could have been ranked lower compared to faulty
% statements. This paper differs from prior work in that it uses a much
% larger dataset of programs and faults and a more rigorous experimental
% methodology.
% %
\section{Conclusions and Future Work}
\label{sec:conc}
%

Several approaches have been proposed in the literature to improve debugging
costs through automated software fault diagnosis to reduce time-to-market,
while maintaining high quality standards. In this domain, Dynamic Slicing (\ds)
and Spectrum-based Fault Localization (\sfl) are very popular fault diagnosis techniques and normally seen as complementary. This paper reports the outcome of
a study using real-world applications with the goal of demystifying the impact
of combining \ds~with \sfl. The results of our empirical study show that, in
practice, \ds~rarely misses faulty statements $9\%$ ($23$ misses in $260$ cases) and that
the \ds-\sfl~combination, coined as \combpar{k},
improves the diagnostic accuracy up to $73.7\%$ ($13.4\%$ on average).
Hence, we found that, despite tacit opinions of the research community about
the usefulness of \ds~in automated debugging, we found the combination practical
and effective, and encourage new \sfl~techniques to be evaluated against that
optimization.

Future work is as follows: improve our oracle heuristics to handle more exceptions;
conduct experiments in more \dfj{} faults or other datasets; find techniques to
handle the cases which harm the cost of diagnosis, such as, faults of omission,
test design problems and the cases which the buggy-class is not in the top-$k$ of 
highest-rank faulty classes.

>>>>

Model-based diagnosis is a well-known approach that has been proposed by the
DX community, a sub-field of AI~\cite{REITER198757,DEKLEER200325}. Applications
of model-based diagnosis to localize software faults have demonstrated that it
can be framed as dynamic slicing~\cite{Mayer:2008:EMM:1642931.1642950,mayer2008prioritising}.
Not many interesting techniques have been pursued due to scalability limitations. We have tackled this using an old program slicing technique --- critical slicing~\cite{DeMillo:1996:CSS:229000.226310}.

Dynamic Slicing has found its main
application in fault
localization~\cite{Agrawal:1990:DPS:93542.93576} on the minimization of failing tests. Research in this area has mainly focused
on slicing code
efficiently~\cite{Wang:2008:DSJ:1330017.1330021,Wang:2004:UCB:998675.999455}
and avoiding data and control omission
errors~\cite{Zhang:2007:TLE:1250734.1250782,Lin:2018:BDE:3238147.3238163}. Dynamic fault localization techniques cannot hope to
soundly report bugs in those cases. The issue is that incorporating
static information to capture those cases can result in unacceptably
large slices, which defeats the purpose of reducing the fault search
space. 
%
% \subsection{SFL}
%
Statistics-based techniques (e.g., ~\cite{Pearson:2017:EIF:3097368.3097441}) are
popular automated fault localization techniques within the Software Engineering
community. They correlate information about program fragments that have been
exercised in multiple program execution traces (also called \textit{program
spectra}) with information about successful and failing executions. By doing
that, statistics-based approaches yield a list of suspect program fragments
sorted by their likelihood to be at fault. Since this technique is efficient in
practice, it is attractive for large modern software systems ~\cite{Zoeteweij:2007:DES:1251988.1253298}.
%
% Spectrum-based fault localization (\sfl{}) is amongst the most common statistical
% fault localization technique that takes as input a test suite including at least
% one failing test and reports on output a ranked list of components likely to be
% in fault ~\cite{7390282,DBLP:conf/kbse/JonesH05,DBLP:journals/smr/LuciaLJTB14,DBLP:journals/jss/AbreuZGG09}.
%
% \subsection{Combination of \sfl{} and Slicing}
%
% Prior work has investigated the combination of dynamic slicing and
% spectrum-based fault
% localization ~\cite{Wotawa:2010:FLB:1848650.1849235,Alves:2011:FUD:2190078.2190115,DBLP:conf/ecai/HoferW12,lei-mao-dai-wang-2012,slicing-sfl-repair}. Although
% the methodology used in these papers vary, the overall message is that
% the combination is valuable. Note that slicing alone does not provide
% the guarantee of improvement to \sfl{} as statements discarded with
% slicing could have been ranked lower compared to faulty
% statements. This paper differs from prior work in that it uses a much
% larger dataset of programs and faults and a more rigorous experimental
% methodology.
% %
\section{Conclusions and Future Work}
\label{sec:conc}
%

Several approaches have been proposed in the literature to improve debugging
costs through automated software fault diagnosis to reduce time-to-market,
while maintaining high quality standards. In this domain, Dynamic Slicing (\ds)
and Spectrum-based Fault Localization (\sfl) are very popular fault diagnosis techniques and normally seen as complementary. This paper reports the outcome of
a study using real-world applications with the goal of demystifying the impact
of combining \ds~with \sfl. The results of our empirical study show that, in
practice, \ds~rarely misses faulty statements $9\%$ ($23$ misses in $260$ cases) and that
the \ds-\sfl~combination, coined as \combpar{k},
improves the diagnostic accuracy up to $73.7\%$ ($13.4\%$ on average).
Hence, we found that, despite tacit opinions of the research community about
the usefulness of \ds~in automated debugging, we found the combination practical
and effective, and encourage new \sfl~techniques to be evaluated against that
optimization.
Future work is as follows: improve our oracle heuristics to handle more exceptions;
conduct experiments in more \dfj{} faults or other datasets; find techniques to
handle the cases which harm the cost of diagnosis, such as, faults of omission,
test design problems and the cases which the buggy-class is not in the top-$k$ of 
highest-rank faulty classes.
